Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
New paper structure with 1 section for each experiment

% !TeX root = ../main-paper.tex
\section{Experimental Setup}

\begin{figure}[tb]
\includegraphics[width=\linewidth]{figs/protocol.pdf}
\caption{Scheme of the evaluation protocol. \joseph{Missing "Ground truth" for NER stage?}}
\label{fig.protocol}
\end{figure}

\subsection{Evaluation protocol \& Metrics}

\Cref{fig.protocol} depicts the evaluation protocol used to assess the OCR and NER systems. Two quality evaluations
are performed in the pipeline, respectively named \emph{OCR Q.A.} and \emph{NER Q.A.}.

First, the layout extraction and entry segmentation of the page are performed with a semi-automated system and
checked by a human. Afterward, an OCR system runs on the thumbnails of each segmented entry to extract its text. An
entry might span over multiple text lines but is always a single block. Thus, the most adapted mode is chosen when
the OCR system allows for the detection mode (e.g. the \emph{block} mode for \emph{Tesseract}).

\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols (hands,
crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V. Rice's
thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip} and the Character Error Rates (CER) are computed at the entry level
and at the global level.

\begin{align}
\mathrm{CER} &=  \frac{\#Errors}{\text{Reference Text Length}} & & \mathrm{CER}_\mathrm{norm} =  \frac{\#Errors}{\text{Alignment Length}} 
\end{align}

In this benchmark, we consider 3 OCR systems well known for historical document analysis: Pero OCR, Tesseract, and Kraken.

Next, a NER system extracts the named entities from the text of each entry output by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on a technique similar as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the precision, recall, and f-measure (or f-score) are computed considering
only the exact matches between entities. Precision and recall are defined by equation (2); the f-measure is their harmonic mean.

@@

The whole process is illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the GOLD text are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the GOLD tags to build the tagged NER reference string. Finally, the NER system runs on the
OCR text; its output is compared to the NER reference string. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/eval-ocr-ner.pdf}
    \caption{OCR and NER evaluation protocol example.}
    \label{fig.eval-ocr-ner}
\end{figure}

\subsection{Experiment 1: NER sensibility to the number of training examples}
\label{subsection:experiment-1-setup}
\bertrand{Find a better name ?}
The constitution of annotated example sets to train a NER model on a target domain is a critical preliminary step.
Often done manually, possibly from bootstrapped annotations, this task is tedious, time-consuming and error-prone.
The ability of a model to perform well even with few training examples is a practical criteria to consider.
In this first experiment, we investigate the performance of the three models when fine-tuned for NER on training sets of decreasing sizes.

To do so, we split the gold reference of manually annotated entries into a training set, a development set, and a test set. 
The training set is then gradually reduced in size while maintaining the relative frequency of directories within it.

@@

% Move to results
%All metrics are evaluated on the test set, yet the biased metrics on the development set are added in the article material as additional information.

\subsection{Experiment 2: Impact of OCR nosie on named entity recognition}
\label{subsection:experiment-2-setup}
Noise introduced by OCR is known to impede the named entity recognition process (see section~\ref{subsection:stoa-ner-on-historical-texts}).
%The second experiment assesses the impact of the OCR on the quality of the NER results.
The second experiment addresses two questions (1) which model is the most robust to OCR noise and (2) what is the most appropriate strategy to fine-tune the NER layer if the input texts to label are noisy ?
To this end, we leverage the labeled OCR datasets produced following to the method explained in Section 5, in addition to the gold reference.

First and foremost, to make sure that the datasets contain the same entries a preprocessing step must be performed.
Indeed, entries where the OCR produced an empty string and those for which no entity could be projected from the gold reference text are ignored.
To overcome this problem we filter each dataset by keeping only the entries common to all.
At the cost of losing  5\% of the gold references entries, we thus have four new annotated datasets containing the exact same entries.
They are denoted hereafter {reference, pero, tesseract}-gold.
Finally each is is split into a training, a dev and a test subset following the procedure presented in\cref{subsection:experiment-1-setup}.

We fine-tune CmBERT and CmBERT+ptrn on reference-gold and pero-gold to create two versions of each model: the former trained on manually corrected entries and the latter on OCR entries.
SpaCy NER is left aside as results from experiment 1 show that it is outperformed by BERT models.
Performance metrics are computed for each of the four resulting NER models against the test sets created from reference-gold, pero-gold and tesseract-gold.

\subsection{Implementation details}

\subsubsection{OCR system parameters}
\nathalie{Y a-t-il des précisions à ajouter sur la façon dont ont été utilisés les OCR? Ou bien ce sont les versions "sur étagère" qui ont servi?}
\joseph{Totalement sur l'étagère. On a normalisé un peu les données après, c'est tout.}
\begin{itemize}
    \item Tesseract 4.1.1 (newest version: 5, released Nov. 2021)
    \item Pero OCR version from git repo, master branch updated on Sep 15, 2021 % 8b20f29    
    \item other?  % kraken if times allows
\end{itemize}

Pero OCR uses ParseNet \joseph{TODO ref} as internal layout parser for line detection.
Pero OCR uses an LSTM engine \joseph{TODO check + ref} for text line recognition.
Pero OCR generally works very well, as long as the bounding boxes of the regions to recognize are not too tightly adjusted.
Trained on newspapers in European languages by its development team.
Can output results in Latin, Greek and Cyrillic scripts, as well as some commonly-used typographic symbols.

% PERO refs
% O Kodym, M Hradiš: Page Layout Analysis System for Unconstrained Historic Documents. ICDAR, 2021.
% M Kišš, K Beneš, M Hradiš: AT-ST: Self-Training Adaptation Strategy for OCR in Domains with Limited Transcriptions. ICDAR, 2021.
% J Kohút, M Hradiš: TS-Net: OCR Trained to Switch Between Text Transcription Styles. ICDAR, 2021.

% \bertrand{Move to results}
%For each size of the training dataset, 5 runs are performed, always with the same parameters, and the mean value of each performance score is computed.

%library and leverage the library utilities to fine-tune it on various training and validation datasets derived from our ground truth dataset (see Section 5.2 for details). The base model is fine-tuned in turn on each of the 8 generated training datasets, using the same training parameters. Early stopping is activated with patience parameters set at 1600. For each size of the training dataset, 5 runs are performed, always with the same parameters, and the mean value of each performance score is computed.

%and Huggingface for the BERT 
%tok2vec(words embeddings + encoding) + attention layer  +  transition-based %model.

\subsubsection{Huggingface CamemBERT}
Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
Its NER head is a linear model with a Softmax function.
CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are performed every 100 steps.

Details can be found for all models in the source code publicly available on the GitHub repository \bertrand{LIEN GITHUB}.

%$BERT_{reference}$ The base model is fine-tuned in turn on each of the training datasets generated from the groundtruth corpus. Training parameters are set depending on the considered experiment: early stopping is activated with the patience parameter set at 3 for experiment 1 and at 5 for experiment 2.

%$BERT_{pero-ocr}$ This model is used for experiment 2 only. The base model is fine-tuned on the training dataset generated by projecting the named entity annotations on the text extracted by PERO OCR, using the same parameters as for the $BERT_{reference}$ model.

%$BERT_{ptrn-reference}$ The base model is pretrained using 845000 entries extracted by PERO OCR with the Next  Sentence  Prediction  (NSP) and  Masked  Language  Model(MLM) tasks. Then it is fine-tuned with the same parameters and on the same training datasets generated from the groundtruth corpus as the $BERT_{reference}$ model.

%$BERT_{ptrn-pero-ocr}$ This model is used for experiment 2 only. The base model is pretrained like the $BERT_{ptrn-reference}$ model and it is fine-tuned with the same parameters and on the same training datasets as the $BERT_{pero-ocr}$ model.

>>>>

% !TeX root = ../main-paper.tex
\section{Experiment 1: NER sensibility to the number of training examples}
\label{sec:ner-xp1}

The constitution of annotated example sets to train a NER model on a target domain is a critical preliminary step.
Often done manually, possibly from bootstrapped annotations, this task is tedious, time-consuming and error-prone.
The ability of a model to perform well even with few training examples is a practical criteria to consider.
In this first experiment, we investigate the performance of the three models when fine-tuned for NER on training sets of decreasing sizes.

\subsection{Dataset}
input: ocr ref (human transcription)
expected output: ner ref (human tagging)

8765 entries, \joseph{FIXME XXXX entities to detect}

\subsection{Metrics}
Next, a NER system extracts the named entities from the text of each entry output by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on a technique similar as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the precision, recall, and f-measure (or f-score) are computed considering
only the exact matches between entities. Precision and recall are defined by equation (2); the f-measure is their harmonic mean.

@@

\subsection{Systems/Variants under test}
We select two deep-learning-based NER models available in packaged software libraries: SpaCy NLP pipelines and CamemBERT.
We also create an additional CamemBERT model pretrained on a collection of unannotated directory entries extracted with Pero-OCR.
The NER layer of each three models is then fine-tuned on historical directories as detailed in \cref{subsection:experiment-1-setup} and \cref{subsection:experiment-2-setup}

\subsubsection{CamemBERT pretrained on directories~[CmBERT+ptrn]}
In order to evaluate the benefits of pre-training the language model on OCR texts from domain-related documents, we adapt the CmBERT embeddings using \num{845.000} entries randomly selected wihtin the collection of directories and extracted with Pero-OCR.
We achieve this by training the CmBERT model for 3 epochs on two unsupervised tasks: next sentence prediction and masked language model.

\subsubsection{Huggingface CamemBERT}
\label{sub:ner-xp1-sysytems-huggingcam}
Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
Its NER head is a linear model with a Softmax function.
CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are performed every 100 steps.

\subsection{Protocol}
To do so, we split the gold reference of manually annotated entries into a training set, a development set, and a test set. 
The training set is then gradually reduced in size while maintaining the relative frequency of directories within it.

@@

\subsection{Results and discussion}

Table \ref{tab:experiment-1-models-performances} and Figure \ref{fig:f1-vs-trainsize} show the mean F1 score, precision, and recall computed on the test dataset, for 5 fine tunings of each model and for each of the 8 training subsets.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the Spacy model.

It appears that pretraining the CamemBERT model on OCRed texts seems worth it only when a the training set used to fine-tune the NER layer is small.
This effect might be due to the differences in nature between the training subsets, whose texts are manually corrected, and the noisy OCR texts used to pretrain CamemBERT.
Indeed, the learned embeddings from the pretraining are specialized on noisy texts and therefore less adapted to clean texts.
The pretraining aims at adapting the model to the vocabulary of the domain and to the errors caused by the OCR, which reveals not helpful and even counter-productive when the texts do not contain these types of errors.

\begin{table}[h!]
\centering
\caption{F1 score, precision and recall measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER in experiment 1 for 8 training sets of increasing sizes.}
\begin{tabular}{llrrrrrrrr}
       & Training examples &  49   &  99   &  199  &  398  &  796  &  1593 &  3186 &  6373 \\
       & \% & 0.8   & 1.6   & 3.1   & 6.2   & 12.5  & 25.0  & 50.0  & 100.0 \\
\midrule\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1 score}} & CmBERT &  89.5 &  90.5 &  92.7 &  93.3 &  \textbf{94.1} &  \textbf{94.9} &  \textbf{94.6} &  \textbf{95.1} \\
       & CmBERT-ptrn &  \textbf{92.2} &  \textbf{92.9} &  \textbf{93.6} &  \textbf{93.8} &  93.8 &  94.1 &  \textbf{94.6} &  94.4 \\
       & SpaCy NER &  87.0 &  89.0 &  90.3 &  91.9 &  92.1 &  92.8 &  93.2 &  93.5 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & CmBERT &  87.4 &  88.7 &  91.5 &  92.7 &  93.3 &  94.9 &  93.9 &  95.1 \\
       & CmBERT-ptrn &  90.8 &  91.8 &  92.9 &  93.0 &  93.0 &  93.4 &  94.1 &  93.9 \\
       & SpaCy NER &  85.6 &  87.7 &  90.0 &  92.0 &  92.4 &  92.8 &  93.1 &  93.7 \\
\cline{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & CmBERT &  91.6 &  92.5 &  93.9 &  93.9 &  94.9 &  94.9 &  95.4 &  95.1 \\
       & CmBERT-ptrn &  93.6 &  94.0 &  94.4 &  94.6 &  94.6 &  94.8 &  95.0 &  94.9 \\
       & SpaCy NER &  88.6 &  90.4 &  90.7 &  91.7 &  91.9 &  92.8 &  93.3 &  93.4 \\
\end{tabular}
\label{tab:experiment-1-models-performances}
\end{table}

\begin{figure}[h!]
	   \center{\includegraphics[width=\textwidth]
	       {images/experiment-1-models-performances.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Precision, recall and f1 score from table~\ref{tab:experiment-1-models-performances}}.
\end{figure}

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
New paper structure with 1 section for each experiment

% !TeX root = ../main-paper.tex
\section{Experimental Setup}

\begin{figure}[tb]
\includegraphics[width=\linewidth]{figs/protocol.pdf}
\caption{Scheme of the evaluation protocol. \joseph{Missing "Ground truth" for NER stage?}}
\label{fig.protocol}
\end{figure}

\subsection{Evaluation protocol \& Metrics}

\Cref{fig.protocol} depicts the evaluation protocol used to assess the OCR and NER systems. Two quality evaluations
are performed in the pipeline, respectively named \emph{OCR Q.A.} and \emph{NER Q.A.}.

First, the layout extraction and entry segmentation of the page are performed with a semi-automated system and
checked by a human. Afterward, an OCR system runs on the thumbnails of each segmented entry to extract its text. An
entry might span over multiple text lines but is always a single block. Thus, the most adapted mode is chosen when
the OCR system allows for the detection mode (e.g. the \emph{block} mode for \emph{Tesseract}).

\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols (hands,
crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V. Rice's
thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip} and the Character Error Rates (CER) are computed at the entry level
and at the global level.

\begin{align}
\mathrm{CER} &=  \frac{\#Errors}{\text{Reference Text Length}} & & \mathrm{CER}_\mathrm{norm} =  \frac{\#Errors}{\text{Alignment Length}} 
\end{align}

In this benchmark, we consider 3 OCR systems well known for historical document analysis: Pero OCR, Tesseract, and Kraken.

Next, a NER system extracts the named entities from the text of each entry output by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on a technique similar as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the precision, recall, and f-measure (or f-score) are computed considering
only the exact matches between entities. Precision and recall are defined by equation (2); the f-measure is their harmonic mean.

\begin{align}
    \mathrm{precision} &= \frac{\text{\#exact matches}}{\text{\#entries in prediction}} & \mathrm{recall} &= \frac{\text{\#exact matches}}{\text{\#entries in reference}}
\end{align}

@@

\subsection{Experiment 1: NER sensibility to the number of training examples}
\label{subsection:experiment-1-setup}
\bertrand{Find a better name ?}
The constitution of annotated example sets to train a NER model on a target domain is a critical preliminary step.
Often done manually, possibly from bootstrapped annotations, this task is tedious, time-consuming and error-prone.
The ability of a model to perform well even with few training examples is a practical criteria to consider.
In this first experiment, we investigate the performance of the three models when fine-tuned for NER on training sets of decreasing sizes.

To do so, we split the gold reference of manually annotated entries into a training set, a development set, and a test set. 
The training set is then gradually reduced in size while maintaining the relative frequency of directories within it.

As the organization and structure of entries varies across directories, the models may learn to overfit on a subset of directories with specific features.
To reduce the evaluation bias, we start by leaving out 3 directories (1690 entries, $\approx 19\%$) from the gold reference to test each model on unseen directories.
Then, a stratified sampling based on the source directory of each entry is run on the remaining set to create a training (6373 entries, $\approx 73\%$ of the gold reference) and a development set (709 entries, $\approx 8\%$).
This sampling procedure is a convenient way to shape both sets, so they reflect the diversity of directories within the gold reference.
The development set is used to evaluate the model performance during the training phase.
To generate smaller training sets, we start from the initial training set and iteratively split it in half using the same stratified sampling strategy as before.
We stop if a directory has only one entry left, or if the current training subset contains less than 30 entries.
Applying this procedure to the initial training set produced 8 training subsets containing 49, 99, 199, 398, 796, 1593, 3186, and 6373 entries.

All tree models are fine-tuned for NER on each training subset.
The performance metrics are measured against the test set after each training.

% Move to results
%All metrics are evaluated on the test set, yet the biased metrics on the development set are added in the article material as additional information.

\subsection{Experiment 2: Impact of OCR nosie on named entity recognition}
\label{subsection:experiment-2-setup}
Noise introduced by OCR is known to impede the named entity recognition process (see section~\ref{subsection:stoa-ner-on-historical-texts}).
%The second experiment assesses the impact of the OCR on the quality of the NER results.
The second experiment addresses two questions (1) which model is the most robust to OCR noise and (2) what is the most appropriate strategy to fine-tune the NER layer if the input texts to label are noisy ?
To this end, we leverage the labeled OCR datasets produced following to the method explained in Section 5, in addition to the gold reference.

@@

\subsection{Implementation details}

\subsubsection{OCR system parameters}
\nathalie{Y a-t-il des précisions à ajouter sur la façon dont ont été utilisés les OCR? Ou bien ce sont les versions "sur étagère" qui ont servi?}
\joseph{Totalement sur l'étagère. On a normalisé un peu les données après, c'est tout.}
\begin{itemize}
    \item Tesseract 4.1.1 (newest version: 5, released Nov. 2021)
    \item Pero OCR version from git repo, master branch updated on Sep 15, 2021 % 8b20f29    
    \item other?  % kraken if times allows
\end{itemize}

Pero OCR uses ParseNet \joseph{TODO ref} as internal layout parser for line detection.
Pero OCR uses an LSTM engine \joseph{TODO check + ref} for text line recognition.
Pero OCR generally works very well, as long as the bounding boxes of the regions to recognize are not too tightly adjusted.
Trained on newspapers in European languages by its development team.
Can output results in Latin, Greek and Cyrillic scripts, as well as some commonly-used typographic symbols.

% PERO refs
% O Kodym, M Hradiš: Page Layout Analysis System for Unconstrained Historic Documents. ICDAR, 2021.
% M Kišš, K Beneš, M Hradiš: AT-ST: Self-Training Adaptation Strategy for OCR in Domains with Limited Transcriptions. ICDAR, 2021.
% J Kohút, M Hradiš: TS-Net: OCR Trained to Switch Between Text Transcription Styles. ICDAR, 2021.

\subsubsection{SpaCy}
We use the French pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the deep-sequoia and wikiner-fr corpora.
The default NER labels known to the pipeline are PER, ORG, MISC and LOC.
In experiment 1 the base model is fine-tuned on every of the 8 training sets using the same training parameters.
Early stopping is activated with a patience value of 1600 training steps without improvement of the f1 score.

% \bertrand{Move to results}
%For each size of the training dataset, 5 runs are performed, always with the same parameters, and the mean value of each performance score is computed.

%library and leverage the library utilities to fine-tune it on various training and validation datasets derived from our ground truth dataset (see Section 5.2 for details). The base model is fine-tuned in turn on each of the 8 generated training datasets, using the same training parameters. Early stopping is activated with patience parameters set at 1600. For each size of the training dataset, 5 runs are performed, always with the same parameters, and the mean value of each performance score is computed.

%and Huggingface for the BERT 
%tok2vec(words embeddings + encoding) + attention layer  +  transition-based %model.

\subsubsection{Huggingface CamemBERT}
Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
Its NER head is a linear model with a Softmax function.
CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are performed every 100 steps.

Details can be found for all models in the source code publicly available on the GitHub repository \bertrand{LIEN GITHUB}.

%$BERT_{reference}$ The base model is fine-tuned in turn on each of the training datasets generated from the groundtruth corpus. Training parameters are set depending on the considered experiment: early stopping is activated with the patience parameter set at 3 for experiment 1 and at 5 for experiment 2.

%$BERT_{pero-ocr}$ This model is used for experiment 2 only. The base model is fine-tuned on the training dataset generated by projecting the named entity annotations on the text extracted by PERO OCR, using the same parameters as for the $BERT_{reference}$ model.

%$BERT_{ptrn-reference}$ The base model is pretrained using 845000 entries extracted by PERO OCR with the Next  Sentence  Prediction  (NSP) and  Masked  Language  Model(MLM) tasks. Then it is fine-tuned with the same parameters and on the same training datasets generated from the groundtruth corpus as the $BERT_{reference}$ model.

%$BERT_{ptrn-pero-ocr}$ This model is used for experiment 2 only. The base model is pretrained like the $BERT_{ptrn-reference}$ model and it is fine-tuned with the same parameters and on the same training datasets as the $BERT_{pero-ocr}$ model.

>>>>

% !TeX root = ../main-paper.tex
\section{Experiment 2: Impact of OCR nosie on named entity recognition}
\label{sec:ner-xp2}
Noise introduced by OCR is known to impede the named entity recognition process (see section~\ref{subsection:stoa-ner-on-historical-texts}).
%The second experiment assesses the impact of the OCR on the quality of the NER results.
The second experiment addresses two questions (1) which model is the most robust to OCR noise and (2) what is the most appropriate strategy to fine-tune the NER layer if the input texts to label are noisy ?

\subsection{Dataset}

To this end, we leverage the labeled OCR datasets produced following to the method explained in Section 5, in addition to the gold reference.

\subsection{Metrics}
prec/recall/F1 as in \ref{sec:ner-xp1}

@@

\subsection{Systems/Variants under test}

\subsubsection{Huggingface CamemBERT}
\joseph{Copie de \cref{sub:ner-xp1-sysytems-huggingcam}. Je suggère de rédiger la section de l'XP 1 en premier et apporter précision nécessaires ici.}

Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
Its NER head is a linear model with a Softmax function.
CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are performed every 100 steps.

\subsection{Protocol}

@@

\subsection{Results and discussion}

CmBERT and CmBERT+ptrn are fine-tuned on the training sets from reference-gold (manually corrected entries) and pero-gold to produce 4 different models.
Their F1 score measured against the test tests from reference-gold, pero-gold and tesseract-gold are given in \cref{fig:exp_2_eval_ner}.
The results clearly show that models perform best when both the pre-training and the NER fine-tuning share the same characteristics (here, OCR noise) as the texts to be processed.

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance the model pre-trained and fine-tuned with pero-gold still gives the best results.
This is probably due to the fact that the texts produced by Pero-OCR feature characteristics intermediary between human transcriptions and Tesseract.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figs/eval-ner-exp2.pdf}
    \caption{F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, either manually corrected or raw from Pero-OCR and Tesseract. The type of examples used to train the NER task is noted in indice after the model name (e.g. Bert$_{reference}$). Results show that best performances on OCRed entries are obtained when the BERT model has been pretrained and fine-tuned for NER on examples affected with similar OCR errors.}
    \label{fig:exp_2_eval_ner}
\end{figure}

### 2022-01-20 src-latex/parts/60-results-BACKUP.tex
New paper structure with 1 section for each experiment

\subcaptionbox{}[.5\linewidth]{
\begin{tabular}{rll}
\toprule
          & CER & CER$_{norm.}$ \\
\midrule
Pero      & 3.78\% & 3.76\% \\   
Tesseract & 6.56\% & 6.45\% \\
Kraken    & 15.72\% & 15.46\% \\  
\bottomrule
\end{tabular}

@@

\includegraphics[width=\linewidth]{images/ocr-eval-2.pdf}
}
\subcaptionbox{}[.5\linewidth]{
\includegraphics[width=\linewidth]{images/ocr-eval-1.pdf}
}
\caption{Character error rates at entry-level for Pero OCR and Tesseract. (a) Global CER and distribution of the CER per entry. (b):
joint plot of the dataset showing that the two systems do not fail on the same entries.}  
\end{figure}

>>>>

\subcaptionbox{}[.5\linewidth]{
\begin{tabular}{rll}
\toprule
          & CER & CER$_{norm.}$ \\
\midrule
Pero-OCR  & 3.78\% & 3.76\% \\   
Tesseract & 6.56\% & 6.45\% \\
Kraken    & 15.72\% & 15.46\% \\  
\bottomrule
\end{tabular}

@@

\includegraphics[width=\linewidth]{images/ocr-eval-2.pdf}
}
\subcaptionbox{}[.5\linewidth]{
\includegraphics[width=\linewidth]{images/ocr-eval-1.pdf}
}
\caption{Character error rates at entry-level for Pero-OCR, Kraken and Tesseract. (a) Global CER and distribution of the CER per entry. (b)
joint plot of the per-entry error rate showing that Pero-OCR and Tesseract do not fail on the same entries.}  
\label{fig.ocr-results}
\end{figure}

\Cref{fig.ocr-results} compares the performance of the OCR systems on our dataset. We can see Kraken's performance are
not as good as the two first OCR. This is partially due to the fact that the closest available model is for English text
and so it misses French specific symbols. On the over hand, even when using a French model trained on French 19th
documents, performance does not increase (and relaxing the character match rules does not help either). Tesseract and
Pero-OCR are performing better on this dataset ``out-of-the-box''. With no fine-tuning, Pero-OCR gets the best accuracy
with less than 4\% character errors. Many of them are even due to a bad line detection in case of multi-lines entries
and are not related to the OCR system itself. \Cref{fig.ocr-results} (b) shows that errors from the two best OCR are not
committed on the same entries (if so, all points would be on the diagonal line) and that combining the outputs of
Pero-OCR and Tesseract would improve the overall recognition quality. Also, we will not consider Kraken in the following
NER experiments because of its recognition rate is already low and cannot be artificially degraded in a controlled setup.
